### 2023-03-28 index.qmd
iniital commit

---
title: "Giovanna Lino"
about:
  template: jolla
  image: testimage.jpg
  links:
    - icon: linkedin
      text: Linkedin
      href: https://www.linkedin.com/in/giovannarlino/
    - icon: github
      text: Github
      href: https://github.com/giovannarlino
---

Hi, I'm Giovanna and I'm a student at the George Washington University. I like business and finance and enjoy keeping up with fashion and italian cuisine.

## Education

B.S. Degree in International Business and Finance from the George Washington University

## Skills

Reporting and Writing

Business Valuation

Marketing strategy

### 2023-03-28 index.qmd
2nd

@@
   template: jolla
-  image: testimage.jpg
+  image: myphoto.jpeg
   links:

### 2023-04-10 about.qmd
1st commit

---
title: "About Me"
---

This website showcases some of my works during my time studying at GW.

```{r}

```

### 2023-04-10 portfolio.qmd
1st commit

---
title: "Portfolio"
---

Hi there this is my portfolio page! Yay...

This is an example of one of my [works](https://www.linkedin.com) during my time at GW.

### 2023-04-10 newsstory.qmd
2nd commit

---
title: "News Story"
---

Article published in the George Magazine for the GW Fashion Business Association. The articles talks about the luxury brand Burberry and its strategies on dealing with sustainability and ESG metrics in a more connected world.

**Burberry: the brand\'s dilemma with sustainability**

The fashion industry is the second largest polluter in the world and consumers are becoming more aware of this. There has been a push to prioritize companies that acknowledge the value of sustainability, and hesitation to support those that fail to address it. Sustainability is a primary concern for consumers and in order for companies to continue to optimize their sales and remain relevant, their designers and managers must address the topic immediately.

When it comes to sustainability, companies have different opinions. On one hand, some argue that becoming sustainable is too costly and not worth the effort. While on the other hand, some brands view this extra cost as something that will be compensated by new clientele. However, it seems that the vast majority of Millenial, Gen X, Gen Z consumers believe that sustainability is a significant issue and that it should be addressed in the fashion industry.

With the influx of these concerned consumers, brands must adjust their strategies and undertake the topic of sustainability to stay competitive. For example, in the luxury fashion industry, fur has always been an important medium. In recent years, there has been a decrease in demand for the luxurious animal by product because there is a heightened awareness of the detrimental effects of the fur industry. For that reason, some designers are beginning to swap fur for something faux. In my opinion, this shift is beneficial and will have a positive impact on a luxury brand\'s reputation.\

One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry. The company proved to be unique in the high fashion market when Thomas created Gabardine, a \'breathable, weatherproof and hardwearing fabric revolutionising rainwear\'. Also adding to the originality of the brand is Thomas Burberry\'s creation of the iconic pattern-based scarves, purses, and trench coats. In 2017, when the company\'s annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year. With the major repercussion of the brand\'s lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change. The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.\

As of now, the brand uses 58% of its energy and 68% of its electricity from clean energy sources and Burberry plans to stay committed to sustainability in the future. The brand has made several promises to become more sustainable for 2022. For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy. In addition, Burberry has released a \'Responsibility Agenda\' to set goals for increasing sustainability within the company. The agenda focuses on three areas: product, company, and communities. Each area is centered on achieving progress by making the brand\'s product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.\

The \'Responsibility Agenda\' goals abides with the Paris Climate Agreement and the UN\'s 17 Sustainable Development Goals. Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company\'s supply chain. The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and \'Bronze Class\' in RobecoSAM\'s 2018 Sustainability Yearbook.\

Furthermore, Burberry established partnerships aimed at increasing sustainability. First, Burberry collaborated with Elvis & Kresse, a sustainable company devoted to rescuing raw materials and transforming it into luxury accessories, to make 120 tons of wasted leather fabric into selling products. Second, the brand has launched a capsule collection made from Econyl, sustainable nylon made from regenerated fishing nets, fabric scraps and industrial plastic, developing a way to combat plastic waste while creating a circular fashion filled with luxury products.

Burberry is one example of a company that suffered political turmoil due to its unsustainable approaches to fashion. Now, the brand is fixing the problem by collaborating with sustainable brands, becoming more transparent with its consumers and stakeholders, and setting goals to increase sustainability at the company. My hope is that Burberry becomes an example for other haute couture to follow.

\

### 2023-04-10 papers.qmd
2nd commit

---
title: "Papers"
---

This is a paper I have written when I took the course called Introduction to International Politics (PSC-1003) at the George Washington University with Professor Downes in 2020. The argument revolves around the bargaining model of countries when they go to war and their negotiations methodologies and techniques. Furthermore, the paper explores the trade offs of those methodologies.

**The Bargaining Model**

War is defined as a "sustained, coordinated violence between political organizations" (Levy & Thompson, 2010, p. 5). As stated in Clausewitz (1996), "the political object is the goal, war is the means of reaching it, and means can never be considered in isolation from their purpose" (p. 87). However, war is not something states normally want. As cited in Fearon (1995), "war can be and often is a product of rational miscalculation" (p. 390), because rational states would normally avoid war due to its high costs. For each state, the value of war is "the share of the good it expects to win, minus the costs it expects to incur" (Frieden, Lake, & Schultz, 2019, p. 98). When states evaluate whether to go to war or to settle, they analyze the costs and values of entering a fight. Assuming that war is costly, states want to avoid it. Therefore, a bargaining range exists. This range is a set of agreements that makes each state at least as well off as it would be by going to war. However, since states live in an anarchic, self-help system there is no credible threat that can enforce states to settle, and without "such credible threat, war will sometimes appear the best option for states that have conflicting interests" (Fearon, 1995, p. 384). The central key for understanding the bargaining model of war is to understand why wars happen if they are so costly. To answer this question the bargaining model assumes five concepts: states are unitary actors that exist in anarchy; states pay the cost of war themselves; states do not prefer war for its own sake; states only care about getting the most valuable deal for themselves; states are rational and weigh costs and benefits. Considering those premises, there are three main reasons for war to occur and for a bargaining range to disappear.

Private information among the international system is one of the key factors that may lead states to war. Given the uncertainty that states face "bargaining strategies that entail a risk of war can be perfectly rational" (Frieden, Lake, & Schultz, 2019, p. 108). This is due to the lack of knowledge that states usually have of their opponent's military power and resolve to fight. When states have access to others' private information, the information needs to be analyzed very carefully, for states may have incentives to misrepresent them, leading their opponents' to overestimate their military power, and underestimate the other's, creating excessive optimism that may prove to be prejudicial in the future. Therefore, states can be misled by others that share misrepresented information in order to hide their weaknesses. States can indeed "exaggerate their true willingness or capability to fight, if by doing so they might deter future challenges or persuade the other side to make concessions. States can also have an incentive to conceal their capabilities or resolve, if they are concerned that revelation would make them militarily vulnerable or would reduce the chances for a successful first strike" (Fearon, 1995, pp. 395-396). Therefore, leaders can have various reasons to misrepresent private information in order to accomplish their goals, and that, in return, may cause the strike of a war. The article of Lake (2010/11) explained the rationalist explanation for the Iraq war using the bargaining theory. The conflict between the US and Iraq can be seen as due to the misrepresentation of information from Iraq. Saddam Hussein could not state the truth about his WMD capabilities to the US, even though he did not have developed any nuclear weapon, because his enemy, Iran, and other domestic opponents would see him as military weak and vulnerable. Moreover, Saddam believed that the US threat to invade Iraq was a bluff because the US lacked resolve, and would only launch a limited attack against the country, meaning that the US lacked credibility when communicating his threat to Saddam. On the other side, the Bush administration was committed to launching an attack against Iraq and did not see any possibility of settlement with the country, underestimating the costs of post-war governance in the US. The bargaining range between these countries disappeared since the US lacked credibility, Iraq had incentives to misrepresent information, and neither side wanted to know about different information that would have challenged each state's prior beliefs and slowed the path to war. In the end, Saddam hid the information regarding Iraq's nuclear weapons, resulting in his removal from power.

The second reason why a bargaining range may not exist relies on one of the most accepted theories that explain that the lack of a bargaining range between states is due to "the difficulty that states can have making credible promises not to use force to revise the settlement at a later date" (Frieden, Lake, & Schultz, 2019, p. 118). This is known as the commitment problem. There exists certain goods that can serve as a source of future bargaining power among states. Therefore, as stated in Frieden, Lake, & Schultz (2019), bargaining over such objects (will make the state) be reluctant to render itself more vulnerable to attack without credible promises that the other state will not exploit that vulnerability in the future (p. 118). This causes a preventive war to happen. As stated in Frieden, Lake, & Schultz (2019), this type of war occurs when there is a lack of balance of military capabilities between states because of factors external to the bargaining process, as a power shift in different rates of economic growth and development of new technologies (p. 120). This signifies that there is a rising state and a declining one. As a result, the weaker state may choose to fight now than to fight in the future when it will be worse off. For instance, consider a state A and a state B. When analyzing the possibility of war, "if B's expected decline in military power is too large relative to B's costs for war, then state's A inability to commit to restrain its foreign policy demands after it gains power makes preventive attack rational for state B" (Fearon, 1995, p. 406). A real life example that combines the concept of private information and commitment problem resulting in a preventive war is the War of Triple Alliance. As state through Weisiger (2013) article, Paraguay feared Argentina's and Brazil's approximation and conquest of Uruguay, stating that those states would threaten to blockade Paraguay's only outlet to the sea. Therefore, Paraguay launched a preventive war against Brazil. Lopez, Paraguay's president, could not commit to any settlement because of his fear of his inevitable decline. In addition, Brazilians believed that Lopez was lying about his reason for attacking the country, so they concluded that Lopez was untrustworthy, unable to commit to any settlement. As a result, Brazil saw the only way to peace as a change in Paraguay's regime by war. There was no bargaining range from either countries as Paraguay held a strong commitment problem. In addition, private misrepresented information also contributed to the downfall of Lopez. During the war, Paraguay only attacked Argentina due to the private information Lopez received that Argentinians would not follow war against the country in case he attacked Argentina. Therefore, Lopez overestimated his chances of winning and attacked Argentina as well. To his surprise, Lopez's private information was false, and Argentinians fought against Paraguay, contributing to its defeat.

Another concept that favors the idea that it is hard for states to credibly commit to a deal is the offensive advantage, through geography or military technology, that some states may have. These advantages help states strike a preemptive war, for when "first-strike advantages are large, both states must be given more from the peacetime bargain in order to allay the greater temptation of unilateral attack" (Fearon, 1995, p. 403). Therefore, states facing this situation are not concerned on making settlements with each other, but are instead focused on which state will strike first, and "negotiations in this context may be seen as nothing more than a ploy to delay the other side from mobilizing" (Frieden, Lake, & Schultz, 2019, p. 125). For instance, the Six Day War between Israel and the four Arab States (Egypt, Syria, Jordan, and Iraq) was a preemptive war. According to Frieden, Lake, & Schultz (2019), Egypt imposed a partial blockade on Israeli border with Syria in response to Israel's conflict with the border country (p. 125). Israel felt that Egypt would attack, and saw the opportunity of a first-strike advantage, even though Egypt did not plan to fight. This eliminated any possible bargaining range between states, for Israel now thought that the only way to solve the situation was to strike a first attack. Therefore, Israel launched a surprise attack on Egyptian air force, destroying Egypt's main offensive weapon, and beginning to control a large territory formerly held by Arabs.

The third and last reason why the bargaining range may disappear relates to the indivisibility of a good. Some goods may not be divided among states without losing their value. This is an all or nothing bargaining situation, and "if both states prefer war over getting nothing, then war becomes inevitable" (Frieden, Lake, & Schultz, 2019, p. 127). For instance, Jerusalem is a piece of land that "contains some of the holiest sites of Christianity, Islam, and Judaism, and historical, cultural, and religious significance unlike any other piece of territory in the world" (Frieden, Lake, & Schultz, 2019, p. 128). Therefore, Jerusalem stands as an obstacle to the resolution of conflicts in the Middle East. How to divide the territory and how to ensure that every religion has access to their holy sites is a question that is long for being resolved. That is one of the reasons why countries usually result to war when fighting for this land, for there is no way to 'divide' the territory for every religion without losing the territory's value. Although Jerusalem today is opened for every religion, each would prefer to have the territory for its own. Therefore, Jerusalem is a land that contributes to the religious/territorial conflict in the Middle East.

The bargaining model can also be applied to a current conflict in the world: the North Korea vs. US conflict. According to Frieden, Lake, & Schultz (2019), it is unknown what North Korea seeks to accomplish when developing nuclear weapons, and there exists different perspectives on how the US should deal with the country's approach to nuclear power (pp. 104-105). On the one hand, some people argue that is not possible to negotiate a bargain with North Korea due the state's commitment problems. The fact that nuclear weapons are a way to reunify Korean peninsula by force reinstates how valuable these weapons are to North Korea and how unlikely negotiations for disarmament will succeed. These people also argue that negotiations in this case serve only to buy North Korea more time to develop its nuclear program, relating to the concept of preemptive war. Another point they make is regarding North Korea's easiness to cheat to any commitment since the country has an autocratic secret regime, making it easy for it to misrepresent information about its nuclear disarmament. Therefore, North Korea is an untrustworthy country. Contributing to this distrust is North Korea's history of breaking deals with the US.

On the other hand, some people believe that North Korea develops nuclear weapons because of Kim Jong-Un's fear of being overthrown from power by the US. In that way, negotiations might work, but only if Washington commits not to seek regime change if North Korea lowers its defense, and commits to promote economic assistance and development in the North Korean regime and to reduce US military in Japan and South Korea. President Trump has been advised with different opinions on the matter. Some of his advisors believe that Trump and his allies should put pressure on North Korea to disarm, including having a limited military strike to convince Kim Jong-Un of the costs of defiance by a broader attack designed to eliminate his arsenal. Other advisors, however, believe that this aggressive measure is counterproductive and risky. If North Korea is interested solely in its own survival, then just the threat of retaliation by the US can deter North Korea from using nuclear weapons. In this conflict, the bargaining model is very controversial. Although, there are various set of possible deals between these two countries, one thing is certain, since both countries possess nuclear power, the possibility of war imposes too many costs for it to be gambled. For that reason, Trump is trying to find the most reasonable deal with North Korea to avoid any war from occurring. The reasons for this conflict sometimes to appear not to have any bargaining range is due to North Korea's commitment problems and misrepresentation of information. However, the consequences of not finding any settlement may result in a nuclear war. Therefore, there needs to exist a bargaining range, for negotiating with North Korea seems as the best diplomatic and rational approach for the resolution of the conflict.

The bargaining model does provide a credible explanation for the causes of war. However, it fails to explain certain aspects that may also lead or not to a conflict. First, the model does not consider postwar costs that may influence a state's decision of going to war or to settle. Second, the theory does not take into account the first image of analysis. Leaders may have motivated and unmotivated biases and specific personalities that may lead states not to have a bargaining range with others. Third, the model does not consider the domestic politics of states such as the regime type, special interests, military influence, and socio-economic problems that may make a country more risk accepting and make it go to war, or more risk-averse and make it prefer any settlement over war. At last, the bargaining model does not take into account multiple states in the brink of war, only two. Therefore, it does not explain how multiple states bargain, and the causes for the occurrence of war among them. As a result, although the bargaining model fails to address other relevant factors when analyzing the causes of war as postwar costs, cognitive biases of decision-makers, states' domestic politics, and conflicts among multiple states, the model provides a good set of explanations for the origins of conflict between two states.

\`\`\`

### 2023-04-10 censusmap.qmd
3rd commit

---
title: "Census Map"
author: "Giovanna Lino"
---

## **Introduction**

In this walkthrough, I will demonstrate how to create an interactive county census map of a chosen state using R. Specifically, I will be using the **`tidycensus`** package to download census data from the American Community Survey and the **`tmap`** and **`mapview`** packages to create the interactive map.

I have chosen the state of Texas and will be mapping the percentage of individuals over the age of 25 with a bachelor's degree or higher.

## **Step 1: Install Packages**

First, make sure you have the necessary packages installed and loaded. In this case I have used the following packages:

```{r}

install.packages("tidycensus")
install.packages("tmap")
install.packages("mapview")

# Load packages
library(tidycensus)
library(tmap)
library(mapview)
library(dplyr)

```

## **Step 2: Set up Census API Key**

To download data from the American Community Survey using the **`tidycensus`** package, you need to set up a Census API key.

With the API key,set it up in R using the following code:

```{r}
# Census API key
#Retrived from the API Link on their page 
census_api_key("75fa32dac9122cf2c43fb6e5d0ed1e7ead626185")

```

## **Step 3: Download Census Data**

Download the census data for Texas using the **`tidycensus`** package. Specifically, we will be downloading the percentage of individuals over the age of 25 with a bachelor's degree or higher.

```{r}

# Download census data
tx_census <- get_acs(
  geography = "county",
  variables = "B15003_022",
  state = "TX",
  survey = "acs5",
  year = 2019)

```

## **Step 4: Join Census Data with Spatial Data**

Now, join the census data with spatial data for Texas counties. We will be using the **`tigris`** package to get the county shapefiles and join them with the census data using the **`left_join`** function.

```{r}

# Load tigris package
library(tigris)

# Texas county shapefiles
tx_counties <- counties(state = "TX", cb = TRUE)

# Join census data with spatial data
tx_map_data <- left_join(tx_counties, tx_census, by = c("NAME" = "NAME"))
```

## **Step 5: Create Choropleth Map**

Create a choropleth map of our data using the **`tmap`** package.

```{r}

tm_shape(tx_map_data) +
  tm_polygons(variables = "B15003_022",
              col = "grey", 
              border.col = "black",
              style = "quantile",
              palette = "Blues",
              title = "Percentage of Individuals with more than 25 with Bachelor's Degree or Higher") +
  tm_layout(main.title = "Texas Counties",
            legend.outside = TRUE)

```

### 2023-04-11 censusmap.qmd
4th

@@
   survey = "acs5",
-  year = 2019)
+  year = 2019,
+  geometry = TRUE)
 
@@
 
-tm_shape(tx_map_data) +
-  tm_polygons(variables = "B15003_022",
-              col = "grey", 
+tm_shape(tx_census) +
+  tm_polygons("estimate",
               border.col = "black",

### 2023-04-11 newsstory.qmd
3rd commit
4th

@@
 title: "News Story"
+author: "Giovanna Lino"
 ---
@@
 
-**Burberry: the brand\'s dilemma with sustainability**
+**Burberry: the brand's dilemma with sustainability**
 
@@
 For that reason, some designers are beginning to swap fur for something faux.
-In my opinion, this shift is beneficial and will have a positive impact on a luxury brand\'s reputation.\
+In my opinion, this shift is beneficial and will have a positive impact on a luxury brand's reputation.\
 
 One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry.
-The company proved to be unique in the high fashion market when Thomas created Gabardine, a \'breathable, weatherproof and hardwearing fabric revolutionising rainwear\'.
-Also adding to the originality of the brand is Thomas Burberry\'s creation of the iconic pattern-based scarves, purses, and trench coats.
-In 2017, when the company\'s annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year.
-With the major repercussion of the brand\'s lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change.
+The company proved to be unique in the high fashion market when Thomas created Gabardine, a 'breathable, weatherproof and hardwearing fabric revolutionising rainwear'.
+Also adding to the originality of the brand is Thomas Burberry's creation of the iconic pattern-based scarves, purses, and trench coats.
+In 2017, when the company's annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year.
+With the major repercussion of the brand's lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change.
 The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.\
@@
 For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy.
-In addition, Burberry has released a \'Responsibility Agenda\' to set goals for increasing sustainability within the company.
+In addition, Burberry has released a 'Responsibility Agenda' to set goals for increasing sustainability within the company.
 The agenda focuses on three areas: product, company, and communities.
-Each area is centered on achieving progress by making the brand\'s product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.\
+Each area is centered on achieving progress by making the brand's product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.\
 
-The \'Responsibility Agenda\' goals abides with the Paris Climate Agreement and the UN\'s 17 Sustainable Development Goals.
-Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company\'s supply chain.
-The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and \'Bronze Class\' in RobecoSAM\'s 2018 Sustainability Yearbook.\
+The 'Responsibility Agenda' goals abides with the Paris Climate Agreement and the UN's 17 Sustainable Development Goals.
+Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company's supply chain.
+The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and 'Bronze Class' in RobecoSAM's 2018 Sustainability Yearbook.\
 

### 2023-04-17 virginiaelectionresults.qmd
another commit

---
title: "Virginia Election Project"
author: "Giovanna Lino"
execute:
  echo: true
format:
  html:
    self-contained: true
    code-tools: true
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}

library(tidyverse)
library(janitor)
library(httr)
library(jsonlite)
library(kableExtra)
library(here)
options(scipen = 999)
options(stringsAsFactors = FALSE)

# library(knitr)
# # print everything as paged ----
# knit_print.data.frame <- function (x, options, ...) {
#   rmarkdown::paged_table(x, options) |>
#     rmarkdown:::print.paged_df()
# }
# registerS3method("knit_print", "data.frame", knit_print.data.frame)

```

# Getting 2020 Presidential results

Data available here: <https://historical.elections.virginia.gov/elections/view/144567/>

A little column cleaning and we'll load in the data file.

```{r}

prez_2020 <- read_csv("processed_data/va_2020_prez_cleaned.csv")

```

Let's see what we have

```{r}

head(prez_2020)

```

Calculating percentage of the vote

```{r}

prez_2020 %>% 
  mutate(
    biden_pct = biden/total_votes_2021_prez
  )

```

Now let's do some rounding and move that decimal point

```{r}

prez_2020 %>% 
  mutate(
    biden_pct = janitor::round_half_up(biden / total_votes_2021_prez * 100, 1)
  )

```

Now trump too

```{r}

prez_2020 <- prez_2020 %>% 
  mutate(
    biden_pct = janitor::round_half_up(biden / total_votes_2021_prez * 100, 2),
    trump_pct = janitor::round_half_up(trump / total_votes_2021_prez * 100, 2)
  )

head(prez_2020)

```

# Getting 2021 Virginia governor results

Data now available from the state here: <https://historical.elections.virginia.gov/elections/view/147466>.

After the election and for few years after, was only available in JSON format.

<https://results.elections.virginia.gov/vaelections/2021%20November%20General/Json/Governor.json>

But site location doesn't exist anymore. We can see it using the wayback machine here:

<https://web.archive.org/web/20220806120753/https://results.elections.virginia.gov/vaelections/2021%20November%20General/Json/Governor.json>

We'll use an archived file of the in JSON to learn about how to deal with it that format.

```{r}

jsonfile <- "raw_data/va_gov_json_archived.json"

#using jsonlite package function fromJSON()
this.content <- fromJSON(jsonfile)

#dataframe from just the 6 content 
content_df <- as.data.frame(this.content[[6]])

```

Where are candidates themselves? They are "nested" inside. We'll use `unnest()`to expand things.

```{r}
#unnest
results <- content_df %>%
  unnest(cols = Candidates)

head(results)

```

Unnest again on locality

```{r}

results <- results %>%
  unnest(cols = Locality)

head(results)
```

Great.

We'll give it a new name to make it easier for us and clean the column names, remove extraneous ones.

```{r}

gov_2021 <- results %>% 
  clean_names() %>% 
  select(-precincts_reporting,
         -precincts_participating,
         -last_modified,
         -ballot_order)

head(gov_2021)

```

What's the issue we may have here?

This is actually tidy data which is good - but for comparing the candidates we'd want them on the same row.

## Reshaping

Enter pivot_wider().

We'll get rid of everything we don't need first.

```{r}

gov_2021 <- gov_2021 %>% 
  filter(ballot_name %in% c("Glenn A. Youngkin", "Terry R. McAuliffe")) %>% 
  select(-locality_code,
         -political_party)

gov_2021

```

Now we'll do the spreading out to reshape. One value for each locality

```{r}

gov_2021_wide <- gov_2021 %>% 
  pivot_wider(names_from = ballot_name, values_from = c(votes, percentage))

gov_2021_wide

```

Nice.

This is giving us some pretty long column names. we can change them after the fact using `rename()`. But first let's clean the names to make it easier.

```{r}

gov_2021_wide <- gov_2021_wide %>% 
  clean_names()

head(gov_2021_wide)
```

Now let's rename, and we'll use similar names to what we had earlier in our 2021 results.

```{r}

gov_2021_wide <- gov_2021_wide %>% 
  rename(
    youngkin = votes_glenn_a_youngkin,
    mcauliffe = votes_terry_r_mc_auliffe,
    pct_youngkin = percentage_glenn_a_youngkin,
    pct_mcauliffe = percentage_terry_r_mc_auliffe
  )

head(gov_2021_wide)

```

Bingo.

There's still one potential issue here. Can you see it?

The percentage columns are actually text values, not numbers. And they have that `%` sign in the text too. Let's fix that using a handy function from the readr package, `parse_number()`.

```{r}

gov_2021_wide <- gov_2021_wide %>% 
  mutate(
    pct_youngkin = readr::parse_number(pct_youngkin),
    pct_mcauliffe = readr::parse_number(pct_mcauliffe)
  )

head(gov_2021_wide)
```

Perfect. Problem solved.

# Putting things together - joining

Now we want to actually join things up.

Can we do that? Let's check out our two tables

```{r}

gov_2021_wide

```

```{r}

prez_2020

```

Few quick things to deal with... first let's get rid of the total votes in 2021, we don't need that anymore. But also the locality isn't the same case as in our governor's results, so let's uppercase it.

```{r}

prez_2020 <- prez_2020 %>% 
  mutate(
    locality = str_to_upper(locality)
  ) %>% 
  select(-total_votes_2021_prez)

prez_2020

```

Great. Now we're all ready to join. Or are we?

Look closely at the record counts for our two tables. It looks like the presidential results has an extra record perhaps? Let's investigate.

We can use `anti_join()` to see what's in one table but not the other.

```{r}

anti_join(prez_2020, gov_2021_wide, by = c("locality" = "locality_name"))

```

There's a total row in there! Well we don't want that. Let's take it out.

Also though notice a second county didn't match...want to be that might be because it's differently worded? Let's see by doing the anti-join in reverse now.

```{r}

anti_join(gov_2021_wide, prez_2020, by = c("locality_name" = "locality"))

```

Yep that's it. So let's fix both of those things in the prez table.

```{r}

prez_2020 <- prez_2020 %>% 
  filter(locality != "TOTALS") %>% 
  mutate(
    locality = str_replace(locality, "KING AND QUEEN", "KING & QUEEN")
  )

```

Now we're ready. Let's join.

```{r}

joined_vacomparison <- inner_join(prez_2020, gov_2021_wide, by = c("locality" = "locality_name"))

head(joined_vacomparison)

#save results to file for next step
saveRDS(joined_vacomparison, here("processed_data", "joined_vacomparison.rds"))
write_csv(joined_vacomparison, here("processed_data", "joined_vacomparison.csv"))

```

Alright! It worked.

## Comparing gov vs. prez results

Now that things are join, let's actually go ahead and start making columns to compare the two elections and how the candidates did this time compared with last time.

Where should we go from here....? Give it a shot...

```{r}

joined_vacomparison %>% 
  mutate(
    mc_overperform = pct_mcauliffe - biden_pct,
    mc_overperform_worsethan5 = if_else(mc_overperform < -5, "YES", "NO") #created a flag column

  )

```

```{r}

#save results to file for next step
saveRDS(joined_vacomparison, here("processed_data", "joined_vacomparison.rds"))
write_csv(joined_vacomparison, here("processed_data", "joined_vacomparison.csv"))

```

# **My Analysis**

```{r}

#load saved joined data file from previous script
joined_vacomparison <- readRDS(here("processed_data", "joined_vacomparison.rds"))

```

# Comparing Virginia Gov vs. President Victory

```{r}

head(joined_vacomparison)

```

```{r}
#what is the average democratic percentage for both presidential and government election in Accomack County?

joined_vacomparison %>% 
  filter(locality == "ACCOMACK COUNTY" ) %>% 
  group_by(biden_pct, pct_mcauliffe) %>% 
  summarise(average = mean(biden_pct)) %>% 
  arrange(desc(average))

```

# **Possible questions to be asked based on the data:**

1.  Create a map of the republican vote in all of the counties for both president and governor.

2.  Analyze the counties with the biggest democratic victory.

3.  Analyze the counties with the biggest republican victory.

4.  Was there a county in which Biden won for which the democratic governor didn't?

### 2023-05-03 about.qmd
annother commit

@@
 
-This website showcases some of my works during my time studying at GW.
+Hello!
+My name is Giovanna Romariz Lino.
+I am 22 years old and I am originally from Londrina, Brazil.
+I have just graduated from George Washington University with a Bachelor of Science degree in Business with a double concentration in International Business and Finance and a minor in Journalism and Mass Communications.
+During university, I have held leadership roles in the Brazilian Student Association, Alpha Kappa Psi Business Fraternity, the GW Socially Responsible Fund, among others.
+I have spent 4 years living in Washington D.C., and I have also studied abroad in Milan, Italy, at Bocconi University during Spring, 2022.
+During my life, I have also lived in Canada, and done summer exchanges in the United States while I was in high school.
+I speak fluent English, Portuguese, intermediate Spanish, and basic Italian.
+I am an only child and my parents still live in Brazil.
 
-```{r}
+During my time at university, I have interned in more than four companies in Brazil focused on finance and marketing.
+I have also participated in consulting projects in Washington D.C.
+My main focuses of work following graduation are on consulting and finance.
+Now, I am moving to New York in July, 2023, and joining Alphasights as an Associate working under their Consulting department.
 
-```
+If you want to know more about my professional experience, you can read my [resume.](https://docs.google.com/document/d/1cv7g5l-lgJfpHSnO49QV12rrD57OgwzQ/edit?usp=sharing&ouid=116938803250525408172&rtpof=true&sd=true)

### 2023-05-03 breakingnewsstory.qmd
annother commit

---
title: "Breaking News Story Sample"
author: "Giovanna Lino"
---

Data:

```{r}

eight_cylinder_cars <- mtcars %>% 
  filter(cyl == 8) %>% 
  nrow()

```

There are `r eight_cylinder_cars` lessons to be learned from the invasion of Ukraine.

"The election today resulted in \_\_\_ counties being won by the Republican candidate"

A new page featuring a sample "breaking news story" that is approximately 250 words and which features at least two pieces of information which are generated using inline R code within your Quarto document. In other words, an example would be "The election today resulted in \_\_\_ counties being won by the Republican candidate" where the \_\_ is filled in on the fly by your inline R code. Note that to accomplish this your Quarto document will have to include the necessary R code chunks above to create the text or number objects you will insert into those spaces.

\
Note that this is an example story you are writing - it can be based off of any dataset you choose to use, either one we've used previously or another you find. All elements needed to complete the code and the narrative must be part of your Quarto document, so whatever dataset you choose will need to be imported into the file at the top, etc, and then crunched appropriately to arrive at the number.\
To take a single value in a dataframe and convert it to a vector, you can use the pull() function if need be.

### 2023-05-03 index.qmd
annother commit

@@
 
-Hi, I'm Giovanna and I'm a student at the George Washington University. I like business and finance and enjoy keeping up with fashion and italian cuisine.
+Hi, welcome to my webiste! I'm Giovanna and I'm a student at the George Washington University.
 
@@
 
-B.S. Degree in International Business and Finance from the George Washington University
+B.S. Degree in Business with a double concentration in International Business and Finance and a minor in Journalism and Mass Communications from the George Washington University in Washington D.C.
 
@@
 
-Reporting and Writing
+Financial analysis and valuation
 
-Business Valuation
+Reporting and writing
 
-Marketing strategy
+Inbound and Outbound Marketing Strategy
+
+## Interests
+
+Business podscasts, italian cuisine and fashion.

### 2023-05-03 newsstory.qmd
annother commit

@@
 
-Article published in the George Magazine for the GW Fashion Business Association.
-The articles talks about the luxury brand Burberry and its strategies on dealing with sustainability and ESG metrics in a more connected world.
+# Voter Suppression in Texas
 
-**Burberry: the brand's dilemma with sustainability**
+*September, 2022*
 
-The fashion industry is the second largest polluter in the world and consumers are becoming more aware of this.
-There has been a push to prioritize companies that acknowledge the value of sustainability, and hesitation to support those that fail to address it.
-Sustainability is a primary concern for consumers and in order for companies to continue to optimize their sales and remain relevant, their designers and managers must address the topic immediately.
+The expression 'Fraudulent Election' has risen into prominence once again as former president Donald Trump has questioned the veracity of the results of the 2020 Presidential Election, when he lost to current Democratic President Joe Biden.
+Texas, a traditional Republican state governed by Greg Abbott, answering to Trump's claims, has passed a Senate Bill tightening state election laws in 2022, which was retaliated with claims of voter suppression in the state of Texas.
 
-When it comes to sustainability, companies have different opinions.
-On one hand, some argue that becoming sustainable is too costly and not worth the effort.
-While on the other hand, some brands view this extra cost as something that will be compensated by new clientele.
-However, it seems that the vast majority of Millenial, Gen X, Gen Z consumers believe that sustainability is a significant issue and that it should be addressed in the fashion industry.
+In light of Abbott's third special season in government, Trump has pressured the current Texas Governor to pursue an election audit in most of the state's counties, claiming voter fraud and irregularities in the 2020 elections.
+Eight and a half hours later, Abbott's administration pursued a forensic auditing process on four of the state's major counties - Collin, Dallas, Harris (Houston included), and Tarrant, showcasing the influence that Trump still has on the state's Republican party.
+However, the vote reassessment did not uncover any impropriety, and there is no evidence of fraud in the state during the election period.
 
-With the influx of these concerned consumers, brands must adjust their strategies and undertake the topic of sustainability to stay competitive.
-For example, in the luxury fashion industry, fur has always been an important medium.
-In recent years, there has been a decrease in demand for the luxurious animal by product because there is a heightened awareness of the detrimental effects of the fur industry.
-For that reason, some designers are beginning to swap fur for something faux.
-In my opinion, this shift is beneficial and will have a positive impact on a luxury brand's reputation.\
+In response to Abbott's actions, Trump wrote a letter claiming that Texans \"do not trust (Abbott's) election system, and they want (his) leadership on this issue, which is the number one thing they care about.\"
 
-One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry.
-The company proved to be unique in the high fashion market when Thomas created Gabardine, a 'breathable, weatherproof and hardwearing fabric revolutionising rainwear'.
-Also adding to the originality of the brand is Thomas Burberry's creation of the iconic pattern-based scarves, purses, and trench coats.
-In 2017, when the company's annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year.
-With the major repercussion of the brand's lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change.
-The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.\
+In September 2021, Abbott signed a senate bill (SB1), which bans 24 hour voting, drive-thru voting, and imposes difficulties on voting for mail-in-ballot, people with disabilities and marginalized groups.
+Those measures also protect partisan poll watchers and set limits to those who help other voters, with their commitment of swearing under oath.
 
-As of now, the brand uses 58% of its energy and 68% of its electricity from clean energy sources and Burberry plans to stay committed to sustainability in the future.
-The brand has made several promises to become more sustainable for 2022.
-For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy.
-In addition, Burberry has released a 'Responsibility Agenda' to set goals for increasing sustainability within the company.
-The agenda focuses on three areas: product, company, and communities.
-Each area is centered on achieving progress by making the brand's product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.\
+"What makes this bill and similar ones Republicans are pushing across the country even more un-American is that Republicans are using the 'Big Lie' about the 2020 election as a pretext to support them.
+The reality is that these bills have nothing to do with election integrity or security, but rather are discriminatory measures making it harder for all people to vote.
+These bills will have a disproportionate impact on communities of color," stated Eric Holder, the US attorney general under former president Barack Obama.
 
-The 'Responsibility Agenda' goals abides with the Paris Climate Agreement and the UN's 17 Sustainable Development Goals.
-Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company's supply chain.
-The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and 'Bronze Class' in RobecoSAM's 2018 Sustainability Yearbook.\
+Democratic candidate for Governor, Beto O'Rourke, has argued in Newsweek that "voter suppression is on purpose and by design, working exactly as Greg Abbott intended".
+He criticized Abbott over reports that election officials have sent back unapproved mail-in-ballot to voters due to identification problems.
+Mail-in-ballots affects voters over 65 years of age who cannot provide a correct driver's license or social security number, military veterans, and overseas voters.
 
-Furthermore, Burberry established partnerships aimed at increasing sustainability.
-First, Burberry collaborated with Elvis & Kresse, a sustainable company devoted to rescuing raw materials and transforming it into luxury accessories, to make 120 tons of wasted leather fabric into selling products.
-Second, the brand has launched a capsule collection made from Econyl, sustainable nylon made from regenerated fishing nets, fabric scraps and industrial plastic, developing a way to combat plastic waste while creating a circular fashion filled with luxury products.
+Furthermore, The New York Times found that after the primaries held in the beginning of 2022, Harris county, the most populous county in Texas, held that "areas with large Black populations were 44 percent more likely to have ballots rejected than heavily white areas." Jen Ramos, the political expert for JOLT Action, a progressive club that works with Texan Latinos, told Newsweek that ballot rejections in El Paso, a city with 85% Latinos, was 15 percent during primaries in 2022.
+The implementation of SB1 has resulted in civil rights groups and democrats filing lawsuits against the new legislation claiming it as an attempt of voter suppression for marginalized communities.
 
-Burberry is one example of a company that suffered political turmoil due to its unsustainable approaches to fashion.
-Now, the brand is fixing the problem by collaborating with sustainable brands, becoming more transparent with its consumers and stakeholders, and setting goals to increase sustainability at the company.
-My hope is that Burberry becomes an example for other haute couture to follow.
+\"Instead of working on issues that actually matter, like protecting school kids from Covid or fixing our failing electrical grid, Abbott is focused on rigging our elections and implementing extreme, right-wing policies,\" said O\'Rourke to The New York Times.
+
+The Gubernatorial Election of Texas in 2022 will be held with no online voter registration on Election Day; stricter ID policies especially for Latinos, communities of color, and people with disabilities, who are less likely to have an acceptable form of identification on hand; no 24 hour election period accommodation; increased limitations for voter's assistants; and stricter criminal penalties.
+
+Abbott's administration continues to claim that the bill facilitates instead of suppresses the voting process, but, with all these obstacles, it is worth questioning the real agenda behind the SB1.
 
 \
+
+\

### 2023-05-03 portfolio.qmd
3rd commit
annother commit

@@
 title: "Portfolio"
+author: "Giovanna Lino"
 ---
 
-Hi there this is my portfolio page! Yay...
+Welcome to my portfolio. Additional past works are included in this [page](https://www.linkedin.com/in/giovannarlino/), which takes you to my Linkedln. profile.
 
-This is an example of one of my [works](https://www.linkedin.com) during my time at GW.
+# **GWFBA**
+
+Articles published in the *George Magazine* for the **GW Fashion Business Association**.
+
+## **Burberry: the brand\'s dilemma with sustainability**
+
+*December, 2020*
+
+The fashion industry is the second largest polluter in the world and consumers are becoming more aware of this.
+There has been a push to prioritize companies that acknowledge the value of sustainability, and hesitation to support those that fail to address it.
+Sustainability is a primary concern for consumers and in order for companies to continue to optimize their sales and remain relevant, their designers and managers must address the topic immediately.
+
+When it comes to sustainability, companies have different opinions.
+On one hand, some argue that becoming sustainable is too costly and not worth the effort.
+While on the other hand, some brands view this extra cost as something that will be compensated by new clientele.
+However, it seems that the vast majority of Millenial, Gen X, Gen Z consumers believe that sustainability is a significant issue and that it should be addressed in the fashion industry.
+
+With the influx of these concerned consumers, brands must adjust their strategies and undertake the topic of sustainability to stay competitive.
+For example, in the luxury fashion industry, fur has always been an important medium.
+In recent years, there has been a decrease in demand for the luxurious animal by product because there is a heightened awareness of the detrimental effects of the fur industry.
+For that reason, some designers are beginning to swap fur for something faux.
+In my opinion, this shift is beneficial and will have a positive impact on a luxury brand\'s reputation.
+
+One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry.
+The company proved to be unique in the high fashion market when Thomas created Gabardine, a \'breathable, weatherproof and hardwearing fabric revolutionising rainwear\'.
+Also adding to the originality of the brand is Thomas Burberry\'s creation of the iconic pattern-based scarves, purses, and trench coats.
+In 2017, when the company\'s annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year.
+With the major repercussion of the brand\'s lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change.
+The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.
+
+As of now, the brand uses 58% of its energy and 68% of its electricity from clean energy sources and Burberry plans to stay committed to sustainability in the future.
+The brand has made several promises to become more sustainable for 2022.
+For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy.
+In addition, Burberry has released a \'Responsibility Agenda\' to set goals for increasing sustainability within the company.
+The agenda focuses on three areas: product, company, and communities.
+Each area is centered on achieving progress by making the brand\'s product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.
+
+The \'Responsibility Agenda\' goals abides with the Paris Climate Agreement and the UN\'s 17 Sustainable Development Goals.
+Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company\'s supply chain.
+The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the \'Textiles, Apparel & Luxury Goods\' sector by the DJSI 2018, and \'Bronze Class\' in RobecoSAM\'s 2018 Sustainability Yearbook.
+
+Furthermore, Burberry established partnerships aimed at increasing sustainability.
+First, Burberry collaborated with Elvis & Kresse, a sustainable company devoted to rescuing raw materials and transforming it into luxury accessories, to make 120 tons of wasted leather fabric into selling products.
+Second, the brand has launched a capsule collection made from Econyl, sustainable nylon made from regenerated fishing nets, fabric scraps and industrial plastic, developing a way to combat plastic waste while creating a circular fashion filled with luxury products.
+
+Burberry is one example of a company that suffered political turmoil due to its unsustainable approaches to fashion.
+Now, the brand is fixing the problem by collaborating with sustainable brands, becoming more transparent with its consumers and stakeholders, and setting goals to increase sustainability at the company.
+My hope is that Burberry becomes an example for other haute couture to follow.
+
+## **Psychedelic Patterns**
+
+*October, 2021*
+
+\
+   Fashion is always trying to reinvent itself.
+During the pandemic, various fashion trends were revived.
+One in particular was psychedelic patterns.
+Inspired by the 70s, this type of print was first popularized by counterculture teenagers in the midst of social and political turmoil.
+The 'LSD fabric' made of colorful lines refers to a 'hallucinogenic\'' pattern that became the inspiration for other psychedelic shapes, and made it possible for the pattern to be produced quickly and appear as a 'groovy' style in movies.
+These patterns are known for their bold colors, sinuous lines and natural shapes.
+
+In 2021, with the use of social media, this style is back in action.
+Tie dye is one of the most popular psychedelic patterns that has been revived.
+According to the trend-forecasting company Heuritech, during this Winter season, tie dye trends are expected to increase more than 6% when compared to previous seasons.  High end brands, along with local boutiques, have embraced this sense of nostalgia and have created collections based on this style.
+Brands such as Tom Ford, Collina Strada, Lecavalier, and Raf Simons have embraced the tie dye and other psychedelic prints in their Spring/Summer 2021 collections.
+
+Raf Simons used colorblocked and defined swirls.
+The collection was named 'Teenage Dreams' inspired by the 1979 film Hair, which resembles the feeling of uncertainty and change that people are living nowadays.
+The pandemic has had a major impact on the return of the psychedelic.
+Dennis Nothdruft, head of exhibitions in the Fashion & Textile Museum in London, said that there is a feeling  of civil unrest and change that correlates with the use of different prints.
+There is nothing more 'youth revolt' than what occurred in the 70s and the current moment we are facing.
+With the return of these prints, there is an evocation for community and participation, providing sensory experiences to the fashion community.
+
+One fashion commentator said that during the pandemic, people got used to looking at social media all the time.
+For a brand to stand out, it requires a creative collection, and nifty patterns are a way to achieve that.
+Ideally, a user would stop scrolling and wonder more about the brand when coming across a stylish psychedelic pattern dress.
+Psychedelic patterns are here to bring back that sense of revolt and freedom that people need in 2021, a freedom that is colorful and bold.
+
+## **Fashion reinvention - Rihanna vs. Savage X Fenty**
+
+*October, 2020*
+
+On September 30, 2020, Rihanna showed her newest Savage X Fenty collection to all fashion lovers.
+Known for having an open and liberal approach to the fashion industry, Rihanna delivered a fashion show filled with diversity and inclusion, with models who identified as men, women, non-binary, and celebrities models as Paris Hilton, Lizzo, Bella Hadid, Normani, Cara Delavigne, Shea Couleé, among many others.
+
+Rihanna started to add to the diversity conversation in fashion when she launched Fenty in 2017, being the first woman of color to be added to the LVMH group.
+From then, she started to portray diversity and body acceptance in all of her collections and fashion shows, and the 2020 fashion show was no different.
+
+During the pandemic, people started to question the meaning of traditional fashion, and how can the industry be more inclusive.
+Quarantine gave people a lot of time to think about this aspect, giving more freedom to reinvent the industry and history of fashion shows.
+Rihanna was one of the designers who invested in this topic and brought to the public a fashion show that empowered people\'s sexuality and encouraged all to take ownership and pride of their bodies when using lingeries.
+
+By taking this inclusive approach, Rihanna impacts not only the fashion industry, but also millions of followers, fans, and consumers who can now envision themselves in all Savage X Fenty lingeries.
+They feel represented, and that is key for both sales success, and, most importantly, for the reinvention of the fashion industry.
+Furthermore, it is necessary to understand that the show is not simply a marketing strategy.
+Rihanna once stated, "I want to make stuff that I can see on the people that I know and they come in all different shapes, sizes, races, religions." It is a part of who she is, and her brand showcases that.
+Therefore, it is more than just an opportunity taken to increase sales by jumping on a trending moment of body acceptance.
+It actually is the core value of the brand and of the designer.
+
+Another concept incorporated in this show was a virtual theatrical experience.
+If you watched it, you know that the show was filled with dancers and performances.
+This unique model enhanced the powerfulness of the show when portraying diversity of genders, races, body heights, and weights.
+It was a very creative approach in comparison to regular fashion shows, especially when it is important to keep consumers\' attention to the show now that it has a virtual format.
+The performance is available on Amazon prime.
+It is shocking how a year ago this was never considered a possibility, and now, it's the new norm.
+
+In a world where Victoria Secrets\' scandal showed that there is still low tolerance when it comes to diversifying lingerie models in the runways, Rihanna questions this status quo with the release of her 2020 Savage X Fenty collection, and does that by capturing its public with an incredible virtual experience!
+
+\
+
+\

### 2023-05-03 virginiaelectionresults.qmd
annother commit

@@
 
-## Comparing gov vs. prez results
+## Comparing gov vs. president results
 
@@
     mc_overperform = pct_mcauliffe - biden_pct,
-    mc_overperform_worsethan5 = if_else(mc_overperform < -5, "YES", "NO") #created a flag column
+    mc_overperform_worsethan5 = if_else(mc_overperform < -5, "YES", "NO")
+    #created a flag column
 
@@
 
+First, I am loading the saved joined data file from the previous script in the code above.
+
 ```{r}
 
-#load saved joined data file from previous script
 joined_vacomparison <- readRDS(here("processed_data", "joined_vacomparison.rds"))
@@
 # Comparing Virginia Gov vs. President Victory
+
+Now, I selected th `joined_vacomparison`\` data to be analyzed, using the head function.
 
@@
 
+Now, I want to find out what is the average democratic percentage for both presidential and government election in Accomack County?
+
 ```{r}
-#what is the average democratic percentage for both presidential and government election in Accomack County?
 
@@
 
-1.  Create a map of the republican vote in all of the counties for both president and governor.
+1.  Analyze the counties with the biggest Democratic victory.
 
-2.  Analyze the counties with the biggest democratic victory.
+2.  Analyze the counties with the biggest Republican victory.
 
-3.  Analyze the counties with the biggest republican victory.
-
-4.  Was there a county in which Biden won for which the democratic governor didn't?
+3.  Was there a county in which Biden won for which the Democratic governor didn't?

### 2023-05-03 walkthrough_R_concept.qmd
annother commit

---
title: " Walkthrough"
format:
  html:
    self-contained: true
---

Here, I am going to walk you through the steps of loading your packages and dataframe, and using functions such as *filter, group_by, mutate and summarise*.

First, I am loading the data and running the code below to create a dataframe called 'impeach'. This dataframe contains a row for every House Democrat and whether the member publicly called for impeachment in the case of the *first* Trump impeachment. There are also other data included related to each politician's district.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load the packages we'll need
library(tidyverse)
library(lubridate)
library(readxl)
library(writexl)
library(janitor)

```

Now, I am running the code to load the dataframe.

```{r}

impeach <- readRDS("impeach.rds")

```

I will take my dataset, *impeach*, and count the amount of members that were in favor of impeachment vs. not in favor. To do that, I first *group_by* for the members in favor, and then I use the *summarise(n())* function to count the amount of members for each category (YES or NO).

```{r}

impeach %>% 
  group_by(for_impeachment) %>% 
  summarise(n())

# In this case, 26 members voted NO vs. 209 voted YES for impeachment

```

Now, I can also include to group not only by the amount of members in favor of Trump's impeachment, but also if the district is above of below the national average for the percentage of people that graduated college. To do that, I follow the same steps as the previous code, but also I add the `pct_bachelors_compared_to_national` in the *group_by* function to count how many districts are above or below national average.

By grouping both those who are in favor and against impeachment and whether the district is above or below the national average the percentage of college graduates, I was able to summarise the count correlating both factors as showed in the table below

```{r}

impeach %>% 
  group_by(for_impeachment, pct_bachelors_compared_to_national) %>% 
  summarise(n())

```

In addition, I can also calculate the mean of something within a data frame. For that, I can take the dataset, group by only the members in favor of impeachment and find the average of college grads that were in favor of impeachment. To do that I first put the data set, *impeach*, then I *group_by* the for_impeachment row, and use the summarise function. Within the summarise function, I assigned the name *average* to become the mean of the `pct_bachelors` row (which showcases the percentage of college grads).

```{r}

impeach %>% 
  group_by(for_impeachment) %>% 
  summarise(average = mean(pct_bachelors))

# Approx. the average 33.7% of college grads are in favor of impeachment and 27.65% are not

```
Another good tool I can use is filtering out only the members who are in favor of the impeachment. Then, after filtering it, I can check how many won their 2018 election by less than 5 percentage points vs. more - which is found in the row `margin_flag_2018`.

For that, I first filter by writing the `for_impeachment` row and assigning it (==) to only equal YES results (those who are in favor of the impeachment). Then, I *group_by* the `margin_flag_2018`, which is where I can find the second part of my data. After, I use the function *summarise (n())* to find the count of members who were in favor of the impeachment *and* have won their 2018 election by 5 percentage points or less vs. more.

```{r}

impeach %>% 
  filter (for_impeachment == "YES") %>% 
  group_by(margin_flag_2018) %>% 
  summarise (n())

# 17 people who were in favor of impeachment won their 2018 election by 5 points or less

```

Furthermore, I can create a new column by usin the function called *mutate()*. In this case, I am creating two new columns, one that will extract the year portion of the column `date_announced` and another which will extract the month of the same column. I have also added the *filter()* function to only select those in favor of the impeachment. I am doing this to find the year and month that people in favor of the impeachment announced their support. Those columns were added as the last ones in the dataframe.

I have also assigned names for the respective functions *year()* and *month()*.

```{r}

impeach %>% 
  filter (for_impeachment == "YES") %>% 
  mutate(year = year(date_announced), month = month(date_announced))

# 2 new columns were created to extract the year and month of the dates announced

```

At last, by using the new columns created with the *mutate()* function, I can again use the *group_by* function to count how many House of Democrats during each month announced their support of impeachment. To do that, I filtered first to only count people who supported the impeachment (the data already only includes House of Democrats), and, with the mutated columns, I grouped by month and summarised the count for eaach one.

```{r}

impeach %>% 
  filter(for_impeachment == "YES") %>% 
  mutate(year = year(date_announced), month = month(date_announced)) %>% 
  group_by(month) %>% 
  summarise(n())

```

### 2023-05-03 breakingnewsstory.qmd
commit again

@@
 author: "Giovanna Lino"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+format:
+  html:
+    self-contained: true
+    toc: true
+    toc-location: left
 ---
 
-Data:
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+
+library(tidyverse)
+library(here)
+```
 
@@
 
-eight_cylinder_cars <- mtcars %>% 
-  filter(cyl == 8) %>% 
-  nrow()
+# Loading the datasets
+counties_demographics <- readRDS(here("counties_demographics.rds"))
+counties_elexresults <- readRDS(here("counties_elexresults.rds"))
 
@@
 
-There are `r eight_cylinder_cars` lessons to be learned from the invasion of Ukraine.
+```{r}
 
-"The election today resulted in \_\_\_ counties being won by the Republican candidate"
+# By joining both datasets, I am grouping/summarizing to calculate the mean pct of Trump 2020 vote by counties above or below the national average for people who identify as nonwhite.
 
-A new page featuring a sample "breaking news story" that is approximately 250 words and which features at least two pieces of information which are generated using inline R code within your Quarto document.
-In other words, an example would be "The election today resulted in \_\_\_ counties being won by the Republican candidate" where the \_\_ is filled in on the fly by your inline R code.
-Note that to accomplish this your Quarto document will have to include the necessary R code chunks above to create the text or number objects you will insert into those spaces.
+nonwhite_voters_average <- inner_join(counties_elexresults, counties_demographics) %>% 
+  group_by(pct_race_nonwhite_abovebelow_natl) %>% 
+  summarise(average = mean(pct_r_2020))
 
-\
-Note that this is an example story you are writing - it can be based off of any dataset you choose to use, either one we've used previously or another you find.
-All elements needed to complete the code and the narrative must be part of your Quarto document, so whatever dataset you choose will need to be imported into the file at the top, etc, and then crunched appropriately to arrive at the number.\
-To take a single value in a dataframe and convert it to a vector, you can use the pull() function if need be.
+nonwhite_voters_average
+
+```
+
+```{r}
+
+#group/summarize to calculate the mean pct of Trump 2020 vote by counties above or below the national average for college graduates (`pct_ed_college_all_abovebelow_natl`).
+
+inner_join(counties_elexresults, counties_demographics) %>% 
+  group_by(pct_ed_college_all_abovebelow_natl) %>% 
+  summarise(average = mean(pct_r_2020))
+```
+
+#  \# `r nonwhite_voters_average` of Trump's voters are part of the counties above national average for people who identify as nonwhite.
+
+In the aftermath of the 2020 Presidential campaign, both the results of the election and the demographics of the voter pool of each county were analyzed for both the Republican candidate Donald Trump and the Democratic candidate Joe Biden.
+Particularly, Trump's mean percentage of votes by U.S.
+counties was analyzed for both the number of nonwhite voters and the number of college graduates and if they were above or below the national U.S.
+average.
+
+It comes as a surprise that more than `r nonwhite_voters_average` of Trump's voters are part of the counties above the national average for people who identify as nonwhite, while approximately 68% of votes are part of counties below the national average for non white-identified people.
+Furthermore, on average, `pct_ed_college_all_abovebelow_natl` of Trump's votes come from counties with people above the national average for college graduates, versus 68% below the national average for college graduates.
+
+These results come as a surprise since it is known that the Democratic party has the majority of college graduate and nonwhite votes.
+Although this is still the case, the Democratic party cannot solely rely on these metrics to ensure victory since more college graduates and nonwhite voters are increasing their support for the Republican party.
+
+This trend can be seen in states such as Texas.
+Some working-class Hispanics do not feel completely represented by the Democratic party in the last gubernatorial race in November, 2022.
+The Democratic candidate, Beto O'Rourke is a citizen of El Paso and has been called out by activists from the organization Sunrise El Paso for not supporting them in their fight against the privatization of their electric companies.
+The city of El Paso is not on the Texas electrical grid, allowing for the company J.P Morgan to privatize it and charge expensive bills.
+Representatives of Sunrise El Paso claim that O'Rourke is too much of a Central Democrat and does not want to compromise the funding of his campaign by selecting fights with big corporations.

### 2023-05-03 virginiaelectionresults.qmd
commit again

@@
 
-# **Possible questions to be asked based on the data:**
+# **Additional analysis from the data:**
 
-1.  Analyze the counties with the biggest Democratic victory.
+1.  **Calculate the Presidential Democratic vote margin and sort by largest margin:**
 
-2.  Analyze the counties with the biggest Republican victory.
+```{r}
 
-3.  Was there a county in which Biden won for which the Democratic governor didn't?
+dem_counties <- joined_vacomparison %>% 
+mutate(dem_margin = biden_pct - trump_pct) %>% 
+arrange(desc(dem_margin))
+
+```
+
+```{r}
+# Show the top 10 counties with the largest Democratic victory
+
+head(dem_counties, 10)
+
+```
+
+2.  **Calculate the Presidential Republican vote margin and sort by largest margin:**
+
+```{r}
+
+rep_counties <- joined_vacomparison %>% 
+mutate(rep_margin = trump_pct - biden_pct) %>% 
+arrange(desc(rep_margin))
+
+```
+
+```{r}
+# Show the top 10 counties with the largest Republican victory
+
+head(rep_counties, 10)
+
+```
+
+3.  **Find any county where Biden won but the Democratic governor didn't:**
+
+```{r}
+
+# subset the data frame to include only counties where Biden won
+biden_counties <- subset(joined_vacomparison, biden_pct > pct_mcauliffe)
+
+# subset the data frame to include only counties where McAuliffe won
+mcauliffe_counties <- subset(joined_vacomparison, pct_mcauliffe > biden_pct)
+
+# find the counties where Biden won but McAuliffe didn't
+biden_only_counties <- subset(biden_counties, pct_mcauliffe == 0)
+
+# print the county names
+print(biden_only_counties)
+
+#In this case, I found that all counties that Biden won, Mcauliffe also won.
+
+```

### 2023-05-09 breakingnewsstory.qmd
final commit

@@
 ---
-title: "Breaking News Story Sample"
+title: "Breaking News Story"
 author: "Giovanna Lino"
@@
 
-```{r}
+```{r, echo=FALSE}
 
@@
 
-```{r}
+```{r, echo=FALSE}
+# By joining both datasets, I am grouping/summarizing to calculate the mean pct of Trump 2020 vote by counties above or below the national average for people who identify as nonwhite.
+
+#Here is the ABOVE value
+
+suppressMessages({nonwhite_voters_average_above <- inner_join(counties_elexresults, counties_demographics) %>% 
+  group_by(pct_race_nonwhite_abovebelow_natl) %>% 
+  summarise(average_above_nonwhite = mean(pct_r_2020)) %>% 
+  filter(pct_race_nonwhite_abovebelow_natl=="ABOVE") %>% 
+  pull(average_above_nonwhite)
+
+nonwhite_voters_average_above_rounded <- round(nonwhite_voters_average_above, 1)
+
+})
+
+```
+
+```{r, echo=FALSE}
 
@@
 
-nonwhite_voters_average <- inner_join(counties_elexresults, counties_demographics) %>% 
+#Here is the BELOW value
+
+suppressMessages({nonwhite_voters_average_below <- inner_join(counties_elexresults, counties_demographics) %>% 
   group_by(pct_race_nonwhite_abovebelow_natl) %>% 
-  summarise(average = mean(pct_r_2020))
+  summarise(average_below_nonwhite = mean(pct_r_2020)) %>% 
+  filter(pct_race_nonwhite_abovebelow_natl=="BELOW") %>% 
+  pull(average_below_nonwhite)
 
-nonwhite_voters_average
+nonwhite_voters_average_below_rounded <- round(nonwhite_voters_average_below, 1)
+})
 
@@
 
-inner_join(counties_elexresults, counties_demographics) %>% 
+#Here is the ABOVE value
+
+suppressMessages({average_pct_ed_college_all_above_natl <- inner_join(counties_elexresults, counties_demographics) %>% 
   group_by(pct_ed_college_all_abovebelow_natl) %>% 
-  summarise(average = mean(pct_r_2020))
+  summarise(average_above_college = mean(pct_r_2020)) %>% 
+  filter (pct_ed_college_all_abovebelow_natl == "ABOVE") %>% 
+  pull(average_above_college)
+
+average_pct_ed_college_all_above_natl_rounded <-  round(average_pct_ed_college_all_above_natl, 1)
+
+})
+
 ```
 
-#  \# `r nonwhite_voters_average` of Trump's voters are part of the counties above national average for people who identify as nonwhite.
+```{r, echo=FALSE}
+
+#group/summarize to calculate the mean pct of Trump 2020 vote by counties above or below the national average for college graduates (`pct_ed_college_all_abovebelow_natl`).
+
+#Here is the BELOW value
+
+suppressMessages({average_pct_ed_college_all_below_natl <- inner_join(counties_elexresults, counties_demographics) %>% 
+  group_by(pct_ed_college_all_abovebelow_natl) %>% 
+  summarise(average_below_college = mean(pct_r_2020)) %>% 
+  filter (pct_ed_college_all_abovebelow_natl == "BELOW") %>% 
+  pull(average_below_college)
+
+average_pct_ed_college_all_below_natl_rounded <-  round(average_pct_ed_college_all_below_natl, 1)
+
+})
+
+```
+
+# **`r nonwhite_voters_average_above_rounded`% of Trump's voters are part of the counties above national average for people who identify as nonwhite.**
 
@@
 Particularly, Trump's mean percentage of votes by U.S.
-counties was analyzed for both the number of nonwhite voters and the number of college graduates and if they were above or below the national U.S.
-average.
+counties was analyzed for both the number of nonwhite voters and the number of college graduates and if they were above or below the U.S.
+national average.
 
-It comes as a surprise that more than `r nonwhite_voters_average` of Trump's voters are part of the counties above the national average for people who identify as nonwhite, while approximately 68% of votes are part of counties below the national average for non white-identified people.
-Furthermore, on average, `pct_ed_college_all_abovebelow_natl` of Trump's votes come from counties with people above the national average for college graduates, versus 68% below the national average for college graduates.
+It comes as a surprise that more than `r nonwhite_voters_average_above_rounded` percent of Trump's voters are part of the counties above the national average for people who identify as nonwhite, while approximately `r nonwhite_voters_average_below_rounded` of votes are part of counties below the national average for non white-identified people.
+Furthermore, on average, `r average_pct_ed_college_all_above_natl_rounded` percent of Trump's votes come from counties with people above the national average for college graduates, versus `r average_pct_ed_college_all_below_natl_rounded` percent below the national average for college graduates.
 
 These results come as a surprise since it is known that the Democratic party has the majority of college graduate and nonwhite votes.
-Although this is still the case, the Democratic party cannot solely rely on these metrics to ensure victory since more college graduates and nonwhite voters are increasing their support for the Republican party.
+Although this is still the case, the Democratic party cannot solely rely on these metrics to ensure victory since more college graduates and nonwhite voters can be switching their minds and increasing their support for the Republican party.
 
 This trend can be seen in states such as Texas.
-Some working-class Hispanics do not feel completely represented by the Democratic party in the last gubernatorial race in November, 2022.
+Some working-class Hispanics did not feel completely represented by the Democratic party in the last gubernatorial race in November, 2022.
 The Democratic candidate, Beto O'Rourke is a citizen of El Paso and has been called out by activists from the organization Sunrise El Paso for not supporting them in their fight against the privatization of their electric companies.
@@
 Representatives of Sunrise El Paso claim that O'Rourke is too much of a Central Democrat and does not want to compromise the funding of his campaign by selecting fights with big corporations.
+The midterm results showcased that O'Rourke lost to Republican candidate Greg Abbott, and that Abbott secured a good portion of votes from the Hispanic community.

### 2023-05-09 censusmap.qmd
another commit
final commit

@@
 #Retrived from the API Link on their page
+
 census_api_key("75fa32dac9122cf2c43fb6e5d0ed1e7ead626185")
@@
 
-# Join census data with spatial data
-tx_map_data <- left_join(tx_counties, tx_census, by = c("NAME" = "NAME"))
 ```

### 2023-05-09 newsstory.qmd
final commit

@@
 
-# Voter Suppression in Texas
+# **Voter Suppression in Texas**
 
@@
 
-In response to Abbott's actions, Trump wrote a letter claiming that Texans \"do not trust (Abbott's) election system, and they want (his) leadership on this issue, which is the number one thing they care about.\"
+In response to Abbott's actions, Trump wrote a letter claiming that Texans "do not trust (Abbott's) election system, and they want (his) leadership on this issue, which is the number one thing they care about."
 
@@
 
-\"Instead of working on issues that actually matter, like protecting school kids from Covid or fixing our failing electrical grid, Abbott is focused on rigging our elections and implementing extreme, right-wing policies,\" said O\'Rourke to The New York Times.
+"Instead of working on issues that actually matter, like protecting school kids from Covid or fixing our failing electrical grid, Abbott is focused on rigging our elections and implementing extreme, right-wing policies," said O'Rourke to The New York Times.
 

### 2023-05-09 portfolio.qmd
final commit

@@
 
-## **Burberry: the brand\'s dilemma with sustainability**
+## **Burberry: the brand's dilemma with sustainability**
 
@@
 For that reason, some designers are beginning to swap fur for something faux.
-In my opinion, this shift is beneficial and will have a positive impact on a luxury brand\'s reputation.
+In my opinion, this shift is beneficial and will have a positive impact on a luxury brand's reputation.
 
 One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry.
-The company proved to be unique in the high fashion market when Thomas created Gabardine, a \'breathable, weatherproof and hardwearing fabric revolutionising rainwear\'.
-Also adding to the originality of the brand is Thomas Burberry\'s creation of the iconic pattern-based scarves, purses, and trench coats.
-In 2017, when the company\'s annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year.
-With the major repercussion of the brand\'s lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change.
+The company proved to be unique in the high fashion market when Thomas created Gabardine, a 'breathable, weatherproof and hardwearing fabric revolutionising rainwear'.
+Also adding to the originality of the brand is Thomas Burberry's creation of the iconic pattern-based scarves, purses, and trench coats.
+In 2017, when the company's annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year.
+With the major repercussion of the brand's lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change.
 The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.
@@
 For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy.
-In addition, Burberry has released a \'Responsibility Agenda\' to set goals for increasing sustainability within the company.
+In addition, Burberry has released a 'Responsibility Agenda' to set goals for increasing sustainability within the company.
 The agenda focuses on three areas: product, company, and communities.
-Each area is centered on achieving progress by making the brand\'s product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.
+Each area is centered on achieving progress by making the brand's product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.
 
-The \'Responsibility Agenda\' goals abides with the Paris Climate Agreement and the UN\'s 17 Sustainable Development Goals.
-Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company\'s supply chain.
-The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the \'Textiles, Apparel & Luxury Goods\' sector by the DJSI 2018, and \'Bronze Class\' in RobecoSAM\'s 2018 Sustainability Yearbook.
+The 'Responsibility Agenda' goals abides with the Paris Climate Agreement and the UN's 17 Sustainable Development Goals.
+Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company's supply chain.
+The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and 'Bronze Class' in RobecoSAM's 2018 Sustainability Yearbook.
 
@@
 Inspired by the 70s, this type of print was first popularized by counterculture teenagers in the midst of social and political turmoil.
-The 'LSD fabric' made of colorful lines refers to a 'hallucinogenic\'' pattern that became the inspiration for other psychedelic shapes, and made it possible for the pattern to be produced quickly and appear as a 'groovy' style in movies.
+The 'LSD fabric' made of colorful lines refers to a 'hallucinogenic'' pattern that became the inspiration for other psychedelic shapes, and made it possible for the pattern to be produced quickly and appear as a 'groovy' style in movies.
 These patterns are known for their bold colors, sinuous lines and natural shapes.
@@
 Quarantine gave people a lot of time to think about this aspect, giving more freedom to reinvent the industry and history of fashion shows.
-Rihanna was one of the designers who invested in this topic and brought to the public a fashion show that empowered people\'s sexuality and encouraged all to take ownership and pride of their bodies when using lingeries.
+Rihanna was one of the designers who invested in this topic and brought to the public a fashion show that empowered people's sexuality and encouraged all to take ownership and pride of their bodies when using lingeries.
 
@@
 This unique model enhanced the powerfulness of the show when portraying diversity of genders, races, body heights, and weights.
-It was a very creative approach in comparison to regular fashion shows, especially when it is important to keep consumers\' attention to the show now that it has a virtual format.
+It was a very creative approach in comparison to regular fashion shows, especially when it is important to keep consumers' attention to the show now that it has a virtual format.
 The performance is available on Amazon prime.
@@
 
-In a world where Victoria Secrets\' scandal showed that there is still low tolerance when it comes to diversifying lingerie models in the runways, Rihanna questions this status quo with the release of her 2020 Savage X Fenty collection, and does that by capturing its public with an incredible virtual experience!
+In a world where Victoria Secrets' scandal showed that there is still low tolerance when it comes to diversifying lingerie models in the runways, Rihanna questions this status quo with the release of her 2020 Savage X Fenty collection, and does that by capturing its public with an incredible virtual experience!
 

### 2023-05-09 walkthrough_R_concept.qmd
final commit

@@
 title: " Walkthrough"
+author: "Giovanna Lino"
 format:
@@
 
-Here, I am going to walk you through the steps of loading your packages and dataframe, and using functions such as *filter, group_by, mutate and summarise*.
+Here, I am going to walk you through the steps of loading your packages and dataframe, and using commands such as *filter, group_by, mutate and summarise*.
+Then, I will also walk you through the concept of *functions* and how to create them using certain data sets.
+
+# **Filter, Group_by, Mutate & Summarise**
 
@@
 ```
+
 Another good tool I can use is filtering out only the members who are in favor of the impeachment.
@@
 ```
+
+# **Functions**
+
+Now, I am going to walk you through the concepts of functions and how to create them.
+First, I create a function that will return the sum of 2 numbers by assigning a name to my function.
+In this case, I assigned 'sum_two_numbers' to my function of number x and y.
+Then, I put 'return' to add both values.
+At last, I add the assign the name 'result' to my sum_two_numbers(5,7) and print the result.
+
+```{r}
+
+sum_two_numbers <- function(x,y){
+
+return(x + y)
+
+}
+
+result <- sum_two_numbers (5,7)
+print(result)
+
+```
+
+Now, I can create a function that will return the mean of a list of numbers fed to it.
+I use the same step as above but instead of summing values, I am generating their mean.
+The 'list' portion refers to the numbers I assigned in the bottom of the code.
+
+```{r}
+
+mean_of_numbers <- function(list){
+  return(mean(list))
+}
+
+list <- c(1,4,6,8,10)
+result <- mean_of_numbers(list)
+print(result)
+
+```
+
+Now, I expand on the function I made above, and instead of just returning the mean number alone, I have it return a sentence. \*"The mean is \_\_\_"\*. (Where the blank is the mean.)
+
+I followed the same steps as above by assigning a name to my function and including a list of numbers in the function.
+After, I just added the text I want generated by using the 'return' and the 'paste0' commands.
+
+```{r}
+mean_of_numbers_with_text <- function(list){
+  return(paste0("The mean is ", mean_of_numbers(list)))
+}
+
+list <- c(1,4,6,8,10)
+result <- mean_of_numbers(list)
+print(result)
+
+```
+
+Another option I did was to create a code that showcases the mean with text.
+I added a list of numbers and generate its mean with the 'mean' command.
+With the 'paste0', I use the text I want printed and the mean I want from the respective list.
+
+```{r}
+numberlist <- c(12,14,15)
+
+resultingmean <- mean(numberlist)
+
+paste0("The mean is ", resultingmean)
+```
+
+Now, we'll use the `flights` dataset from the package `nycflights13`.
+It contains records of individual airline flights departing at New York's three metro airports, JFK, LaGuardia (LGA) and Newark (EWR).
+Run the following chunk to load the data.
+
+```{r}
+install.packages("nycflights13")
+```
+
+```{r}
+#load the data to use for the rest of the assignment questions
+flights <- nycflights13::flights
+
+head(flights)
+```
+
+Using the `flights` dataset, I created a function that filters the data frame to only include records from a single originating airport (column name `origin`).
+
+In other words, it should let you enter an origin airport and return all the records from just that airport.
+Then, I create the function I want by assigning a name to it and return the result.
+In this case I assigned the name 'filter_flights_by_origin'.
+
+```{r}
+#creating the function
+
+airportname <- "LGA"
+
+flights %>% 
+  filter(origin == airportname)
+
+filter_flights_by_origin <- function(airportname) {
+  result <- flights %>% 
+  filter(origin == airportname)
+
+  return(result)
+}
+```
+
+Now, I use the assigned name to only return the values from the origin I selected.
+
+```{r}
+#returning values
+
+filter_flights_by_origin("LGA")
+
+```
+
+Now, using the `flights` data set, I created a function that:
+
+First, filters the data frame to only include records from a single originating airport (column name `origin`)...
+
+```{r}
+airportname <- "LGA"
+
+flights %>% 
+  filter(origin == airportname) %>% 
+  count(carrier)
+```
+
+...
+And then ,aggregates the results by airline (`carrier`) to show how many flights each airline has from that airport.
+Here, I used the filter, count, and function commands.
+I combined all of the steps above into one.
+A different command here is the 'head' command that shows the top value of the list since I included the #1 inside the brackets.
+
+```{r}
+count_byairline_for_one_airport <- function(airportname) {
+  result <- flights %>% 
+    filter(origin == airportname) %>% 
+    count(carrier, sort = TRUE) %>% #sort = TRUE showcases from the highest value to the lowest 
+    head(1) #for the top value of the list
+
+  return(result)
+}
+
+count_byairline_for_one_airport("EWR")
+
+```
